\documentclass[document.tex]{subfiles}
\begin{document}

\addcontentsline{toc}{chapter}{Acknowledgement}

\begin{center}
        \textbf{{\fontsize{16pt}{18}\selectfont ACKNOWLEDGEMENT}}
        \vspace{1cm}
\end{center}


\noindent 
The real spirit of achieving goal is through the way of excellence and discipline. I would never be succeed to complete my task without the co-operation, encouragement and help provided to me by various personalities. \\
First of all, I render my gratitude to my Almighty Allah who bestowed self-confidence, ability and strength in me to complete this work preciously. \\
With deep sense of gratitude I express my sincere thanks to my esteemed and worthy Supervisor, \textbf{Biprodip Pal, Assistant Professor}, Department of Computer Science \& Engineering, Rajshahi University of Engineering \& Technology (RUET), Rajshahi, Bangladesh, for his valuable guidance in carrying out this work under his effective supervision, encouragement, enlightenment and co-operation. Most of the novel ideas and solutions found in this thesis are result of our numerous stimulating discussions. His feedback and editorial comments were also invaluable for writing of this thesis.\\
I want to express my gratitude thanks to \textbf{Dr. Md. Rabiul Islam, Professor, Head of the Department}, Computer Science \& Engineering, Rajshahi University of Engineering \& Technology (RUET), Rajshahi, Bangladesh, for his extending helps in various ways from his department. I also grateful to other teachers of the Department of Computer Science and Engineering, Rajshahi University of Engineering \& Technology (RUET), Rajshahi, Bangladesh for their valuable and constructive suggestions, endless facilitation and inspiration.\\
Finally, yet importantly, I would like to express my heartfelt thanks to my beloved parents for their blessing, my family members for their help and wishes for the successful completion of this work.\\

\vspace*{\fill}

\textbf{{\fontsize{14pt}{17}\selectfont
        \begin{tabular}{>{\raggedright}p{0.5\linewidth}>{\centering}p{0.5\linewidth}}
                December, 2017         & \authorname\tabularnewline 
                RUET, Rajshahi & \tabularnewline            
        \end{tabular}
}}

\clearpage

\end{document}
